---
title: "SL Final Project: IMDB Movie Reviews"
author: "Jake Greenberg - `jgreenberg5342@floridapoly.edu`, Wyatt Smith - `wsmith4725@floridapoly.edu`"
output: 
  html_notebook:
    toc: true
---


# Preparation

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
```

Insert the dataset to be used
```{r, warning=FALSE, message=FALSE}
IMDB <- read_csv("https://raw.githubusercontent.com/wsmith867/SL_Project/master/IMDB_movies.csv")
```

Variable            |    Description                  |
--------------------|---------------------------------|
`Rank`              | IMDB Ranking                    | 
`Title`             | Title Name                      | 
`Genre`             | Category of Movie               | 
`Description`       | Plot Description                | 
`Director`          | Director Name                   | 
`Actors`            | Actor Names                     | 
`Year`              | Year Released                   | 
`Runtime (Minutes)` | Duration in minutes             | 
`Rating`            | IMDB Rating                     | 
`Votes`             | Number of votes received        | 
`Revenue (Millions)`| Total Movie Sales               | 
`Metascore`         | Metascore Rating (Out of 100)   | 


```{r}
IMDB %>% 
  sample_n(10)
```





